On the presentation of orthogonal groups over polynomial rings

### 2019-07-23 dl-paper.tex
Added definition of crossed modules

Let us describe the procedure for relativization as specified by Loday.
Let $S \colon \catname{CRings} \to \catname{Groups}$ be a functor.
Set $G_i = \Ker(S(p_i))$ and define Loday's relativization $S(R, I)$ as $ G_0 / [G_0, G_1]$. The map $S(p_1)$ induces a natural transformation $S(R, I) \to S(R)$. 
For the sake of shortness we denote this map by $\mu = \mu_{R,I}$. In fact, there is a natural exact sequence:
\begin{equation}
 \xymatrix{ 1 \ar[r] & C(R, I) \ar[r] & S(R, I) \ar^{\mu}[r] & S(R) \ar[r] & S(R/I) \ar[r] & 1}
\end{equation}
\begin{example}
 If one applies Loday's relativization to the functor $S(R) = \St(R)$ one recovers the usual relative Steinberg group $\St(R, I)$
  as defined in~\cite{Kbook}[Ch. III, Definition~5.7]. Notice that $\St(R, I)$ is not a subgroup of $\St(R)$ but rather its central extension.
\end{example}

>>>>

Let us describe the procedure for relativization as specified by Loday.
Let $S \colon \catname{CRings} \to \catname{Groups}$ be a functor.
Set $G_i = \Ker(S(p_i))$ and define Loday's relativization $S(R, I)$ as $ G_0 / [G_0, G_1]$. The map $S(p_1)$ induces a natural transformation $S(R, I) \to S(R)$. 
For the sake of shortness we denote this map by $\mu = \mu_{R,I}$. We also introduce the notation for the kernel of $\mu$.
\begin{equation} \label{LodayRelativization}
 \xymatrix{ 1 \ar[r] & C(R, I) \ar[r] & S(R, I) \ar^{\mu}[r] & S(R) \ar[r] & S(R/I) \ar[r] & 1}
\end{equation}
\begin{example}
 If one applies Loday's relativization to the functor $S(R) = \St(R)$ one recovers the usual relative Steinberg group $\St(R, I)$
  as defined in~\cite{Kbook}[Ch. III, Definition~5.7]. Notice that $\St(R, I)$ is not a subgroup of $\St(R)$ but rather its central extension.
\end{example}

The exact sequence in~\eqref{LodayRelativization} often is an example of a {\it relative central extension}.
Let us briefly recall the relevant terminology. 
First of all, recall that a {\it central extension} of a group $G$ is a surjective map $\widetilde{G} \to G$, whose kernel is contained in the center of $\widetilde{G}$. 
A central extension is said to be {\it universal} if it is an initial object of the category of central extensions of $G$.

Recall that a {\it crossed module} is a triple $(M, N, \mu)$ consisting of a group $N$ acting on itself by left conjugation, an $N$-group $M$ and a map
 $\mu \colon M\to N$ of $N$-groups satisfying {\it Peiffer identity} $\mu(m) \cdot m' = m m' m^{-1}$. It can be shown that the image of $\mu$ is always
  a normal subgroup of $N$ and that the kernel of $\mu$ is always contained in the center of $M$.

Now if $\nu \colon N \twoheadrightarrow Q$ is a surjective map of groups, a {\it relative central extension of $\nu$} is, by definition,
a crossed module $(M, N, \mu)$ such that the cokernel of $\mu$ is precisely $\nu$. Thus, we have the following diagram
\begin{equation} \label{RelativeCentralExtension}
 \xymatrix{ 1 \ar[r] & C \ar^{\lambda}[r] & M \ar^{\mu}[r] & N \ar^{\nu}[r] & Q \ar[r] & 1}
\end{equation}
